# 1. BUSINESS UNDERSTANDING
## a. Defining the question
A cryptography course is being set up with advertisement being done on a Kenyan entrepreneur's blog. Previously, the same entrepreneur's blog; a similar course was advertised and the data was collected. How can the collected data be used to predict the potential individuals most likely to view the adds.

## b. Defining the metric of success

The project shall be deemed successful if a correlation of one factor is matched with the probability of clicking. 

## c. Understading the context
## d. Recording the experimental design

The following shall be used to analyze the data:
1. CoVariance
2. Correlation
3. Measures of central tendency
4. Visualization of the data

## e. Data Relevance
## f. Appropriateness of the data
# 2. DATA AQUISITION AND EXTRACTION, TRANSFORMING AND LOADING
## a. Importing of the libraries
```{r}
library(data.table)
```
### Reading the data
```{r}
library(data.table)
dt = fread('http://bit.ly/IPAdvertisingData')
```

```{r}
head(dt, 10)
```

```{r}
tail(dt, 10)
```
### Understanding of the data
```{r}
dim(dt)
```
```{r}
summary(dt)
```

```{r}
columnnames <- colnames(dt)
columntypes <- c()
noofunique <- c()
for (y in columnnames){
  columntypes <- c(columntypes , class(dt[[y]]))
  noofunique <- c(noofunique, length(unique(dt[[y]])))
}
desc <- data.frame('Column Names' = columnnames , 'Column Types' = columntypes , 'Number of Unique' = noofunique)
desc
```

### Anomalies
```{r}
summary(dt)
```
```{r}
dt$Male <- as.factor(dt$Male)
dt[['Clicked on Ad']] <- as.factor(dt[['Clicked on Ad']])
```
### Outliers
```{r}
columnnames <- colnames(dt)
columntypes <- c()
noofunique <- c()
for (y in columnnames){
  columntypes <- c(columntypes , class(dt[[y]]))
  noofunique <- c(noofunique, length(unique(dt[[y]])))
}
desc <- data.frame('Column Names' = columnnames , 'Column Types' = columntypes , 'Number of Unique' = noofunique)
desc
```

```{r}
cv <- desc[desc$Column.Types == 'integer' | desc$Column.Types == 'numeric',]
numericalcolumns <- cv[['Column.Names']]
for (we in numericalcolumns){
  boxplot(dt[[we]], main = we)
}
```
### Missing data 
```{r}
colSums(is.na(dt))
```
```{r}
dt <- na.omit(dt)
```
### Duplicated data
```{r}
dt <- unique(dt)
```
# 3. EXPLORATORY DATA ANALYSIS
### Univariate 
```{r}
centr <- data.frame(
	'Mean' = apply(dt[, ..numericalcolumns] , 2 , mean),
	'Median' = apply(dt[, ..numericalcolumns], 2 , median),
	#Mode = apply(dt[,1:4], 2 , mode),
	'Maximum' = apply(dt[, ..numericalcolumns], 2 , max),
	'Minimum' = apply(dt[, ..numericalcolumns], 2 , min),
	'Standard Deviation' = apply(dt[, ..numericalcolumns], 2 , sd),
	'Variance' = apply(dt[, ..numericalcolumns], 2 , var)
	)
centr
```
### Bivariate
### Multivariate
# 4. Insights
# 5. Conclusion
# 6. Recommendation